### 2024-06-30 causal-inference.qmd
20240630 - figure sizing

```{r}
#| label: fig-XCausesY
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting *X* Causing *Y*."

@@

plot(dagitty::graphLayout(YCausesX))

@@

::: {#fig-simpsonParadox}
![](images/simpsonParadox.png)

>>>>

```{r}
#| label: fig-XCausesY
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting *X* Causing *Y*."
#| out-width: 20%

@@

plot(dagitty::graphLayout(YCausesX))
```

@@

::: {#fig-simpsonParadox}
![](images/simpsonParadox.png){width=200%}
